---
title       : Presidential Approval Ratings
subtitle    : 
author      : asamuelson
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---s

## App Introduction
With the 2016 US presidential race nearing completion, it is interesting to 
investigate the approval ratings of US presidents in the past. 

This app allows the user to look at presidential approval ratings for the time 
period 1945-1974.

There are a few NAs in the data, which are handled by the app.

--- .class #id

## Presidential Approval Ratings
The presidents dataset in the R datasets library contains a time series based on  
quarterly US presidential approval ratings from the Gallup Organisation. 

According to the R documentation, more information can be found in the following 
reference: McNeil, D. R. (1977) Interactive Data Analysis. New York: Wiley.

--- .class #id

## Data Summary

A brief summary of the data can be found below. 

```{r, echo=FALSE, eval = TRUE}
summary(presidents)
```

```{r, echo=FALSE, eval = TRUE}
plot(presidents, main="Historical Approval Ratings", ylab = "Approval Rating (%)")
```

--- .class #id

## App Functionality

The app allows the user to enter a year and a quarter in the UI and calculates 
the US president's approval rating for that time period. It also plots the mean 
and selected approval ratings to show the user how the approval rating for the 
selected time period comp[ares to the historical average.

The back-end calculation in server.R is used to find and return the data for the
year and quarter from the presidents time series data.
